High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors

### 2012-03-29 paper.tex
Added a small bit about the nummeric model.

SKAL VI SKRIVE NOGET OM FLYVETID-TIL-MASSE OMREGNING?
The model is bla bla bla and can freely be acquired\cite{ModelGithub}.
\begin{figure}
 \includegraphics[width=14cm]{model_error.png}%
 \caption{In the top panel a plot of the flight time as a function of mass is shown. The red full line is fitted to calculated model points (blue dots) to relate mass to flight time in the TOF-MS. In the bottom figure the difference between acquired experimental data and data calculated from the model is plotted. As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
\end{figure}

>>>>

Since the TOF-MS only measures flighttime and not the actual mass of the measured molecules, it is necessary to have a way to calculate back and forth between flight time and mass. This can be done by finding known patterns in the mass-spectrum where the masses can be resonably dertimed from experience and then fit these values to get an expression for the flighttime as a function of mass. This method works fine, but does have the drawback that it is necessary to have several peaks of well known mass, which is not always necessarily the case. For this reason we have also made a small nummeric model of the mass spectrometer, which will calculate the flight time based only on the voltages for the pulser, liner and reflectron and thus provides a dertermination of the time to mass conversion. Typically the model is used together with the experimental determination of a single mass, since this will help fix the unkown delay between measurement trigger and the rise of the high-voltage pulse at the repeller plate. As seen in Figure~\ref{fig:model_error} the performance of the model is surprisingly good considering its simplicity. The model can freely be acquired\cite{ModelGithub}.
\begin{figure}
 \includegraphics[width=14cm]{model_error.png}%
 \caption{Comparison of the simulated model (red line, top panel) to actual measured experimental values (blue dots). In the bottom panel the difference between acquired experimental data and data calculated from the model is plotted, errorbars represents only the uncertainty in the experimental data. As seen from the figure a deviation of $\sim$100\,ns at 70\,amu is present.\label{fig:model_error}}%
\end{figure}
